### 2014-11-06 tex/proofs.tex

After initialization, \textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} for $\rgse$ creates a new heap
$(\cfgnt{L}^\prime_p [\cfgnt{r}^\prime \mapsto \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime_p$

and for $\rsym$ it relates the state 
$$ 
s_\sym^\prime = \lp \cfgnt{L}_{s}[\cfgnt{r}^\prime \mapsto \mathbb{VS}\lp \cfgnt{L}_{s},\cfgnt{R}_{s},\cfgnt{r},\cfgnt{f},\phi_g\rp ]\ \cfgnt{R}_{s}\ \phi_g\ \eta\ \cfgnt{r}^\prime\ \cfgnt{k}\rp 
$$

The functional in \defref{} requires and forward
\eqref{eqn:BisimulationForwards} and backward
\eqref{eqn:BisimulationBackwards} relationship between successor
heaps.

>>>>

After initialization, \textrm{F{\footnotesize IELD}}
\textrm{A{\footnotesize CCESS}} for $\rgse$ relates a new heap in any
successor state as $(\cfgnt{L}^\prime_p [\cfgnt{r}^\prime \mapsto
  \lp\phi^\prime\ l^\prime\rp]\ \cfgnt{R}^\prime_p)$, and for $\rsym$ it
relates the heap in the only successor state as $(\cfgnt{L}^\prime_q[\cfgnt{r}^\prime \mapsto
  \mathbb{VS}\lp
  \cfgnt{L}^\prime_q,\cfgnt{R}^\prime_q,\cfgnt{r},\cfgnt{f},\phi_g\rp
]\ \cfgnt{R}^\prime_q)$; each version adding in the constraint-location pair or
value set respectively on the same reference $\cfgnt{r}^\prime$.

The functional in \defref{bisimulation} requires and forward
\eqref{eqn:BisimulationForwards} and backward
\eqref{eqn:BisimulationBackwards} relationship between successor
heaps.
